Fourmile Calibrations and Output

### 2024-10-08 fourmile_outputs_2013edits.Rmd
fxied winter cumulative p hru plot

precip_jan <- ggplot() +
  geom_sf(data = hrus_map_precip_jan, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

@@

precip_apr <- ggplot() +
  geom_sf(data = hrus_map_precip_apr, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')
##

@@

precip_jul <- ggplot() +
  geom_sf(data = hrus_map_precip_jul, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

@@

precip_sep <- ggplot() +
  geom_sf(data = hrus_map_precip_sep, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

>>>>

precip_jan <- ggplot() +
  geom_sf(data = hrus_map_precip_jan, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 9.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

@@

precip_apr <- ggplot() +
  geom_sf(data = hrus_map_precip_apr, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 9.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')
##

@@

precip_jul <- ggplot() +
  geom_sf(data = hrus_map_precip_jul, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 9.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

@@

precip_sep <- ggplot() +
  geom_sf(data = hrus_map_precip_sep, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 9.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')
